External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-12 CVPR2017_Review_Unified.tex
add

Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems. In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging. In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise. Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3.5mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of a cropped part from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

@@

Image priors are playing a key role in image denoising \cite{pgpd,epll,ksvd,ple,ncsr,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{foe,pgpd,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images. In this paper, we use external priors to guide the internal prior learning.\ Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.

@@

Recently, several image denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}. Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
{\footnotesize (f) NC \cite{noiseclinic}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
{\footnotesize (g) NI \cite{neatimage}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\vspace{-3mm}
\caption{Denoised images of the real noisy image ``Dog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\vspace{-1mm}
\label{fig6}
\end{figure*}

@@

We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.\ Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.\ We use the method in \cite{noiselevel} to estimate the noise level for them.\ All the other parameters in these methods are set as the default ones.\ Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.

@@

\vspace{-2mm}
\subsubsection{Comparison on Dataset \cite{crosschannel2016}}

As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms. We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}. The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic} and
CC \cite{crosschannel2016} are listed in Table \ref{tab2}. (The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold. One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons can be found in the supplementary file.

@@

\begin{table}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\vspace{-3mm}
\label{tab3}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
\\
\hline
PSNR &   34.58 & 34.52 & 36.19 & 37.40
\\
\hline
Methods& \textbf{TNRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
\\
\hline
PSNR &  {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
%SSIM &   0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 37.00dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 37.02dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 37.01dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 33.90dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 36.18dB  } 
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
{\footnotesize (f) NC \cite{noiseclinic}: 38.76dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.68dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 38.37dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
{\footnotesize (i) Ours: \textbf{40.50}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of a part cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images 
\vspace{-0.5mm}
are better to be zoomed in on screen.}
\vspace{-1mm}
\label{fig7}
\end{figure*}

>>>>

Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems. In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging. In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise. Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{ncsr,nlm,bm3d,cbm3d,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3.5mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of a cropped part from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

@@

Image priors are playing a key role in image denoising \cite{ksvd,ncsr,pgpd,epll,ple,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{pgpd,foe,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images. In this paper, we use external priors to guide the internal prior learning.\ Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.

@@

Recently, several image denoising methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}. Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
{\footnotesize (f) NC \cite{noiseclinic,ncwebsite}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
{\footnotesize (g) NI \cite{neatimage}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\vspace{-3mm}
\caption{Denoised images of the real noisy image ``Dog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\vspace{-1mm}
\label{fig6}
\end{figure*}

@@

We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic,ncwebsite}, Neat Image (NI) \cite{neatimage}, and Cross-Channel (CC) \cite{crosschannel2016}.\ Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.\ We use the method in \cite{noiselevel} to estimate the noise level for them.\ All the other parameters in these methods are set as the default ones.\ Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.

@@

\vspace{-2mm}
\subsubsection{Results on Dataset \cite{crosschannel2016}}

As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms. We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}. The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic,ncwebsite}, NI \cite{neatimage} and
CC \cite{crosschannel2016} are listed in Table \ref{tab2}. (The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold. One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons can be found in the supplementary file.

@@

\begin{table}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\vspace{-3mm}
\label{tab3}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
\\
\hline
PSNR &   34.58 & 34.52 & 36.19 & 37.40
\\
\hline
Methods& \textbf{TNRD}& \textbf{NC} & \textbf{NI} &\textbf{Ours} 
\\
\hline
PSNR &  {\color{blue}{37.75}} & 37.57  & 36.53 & {\color{red}{ 38.75}}
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 37.00dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 37.02dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 37.01dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 33.90dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 36.18dB  } 
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
{\footnotesize (f) NC \cite{noiseclinic,ncwebsite}: 38.76dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.68dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 38.37dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
{\footnotesize (i) Ours: \textbf{40.50}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of a part cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images 
\vspace{-0.5mm}
are better to be zoomed in on screen.}
\vspace{-1mm}
\label{fig7}
\end{figure*}
